Temporal Split

### 2023-01-30 workflow/notebooks/temporal-split.Rmd
Plot 100x performance alongside temporal split

```{r perf_100x}
perf_dat_100 <- data.table::fread(here('results', 
                                      'performance_results_aggregated.csv')
                                 ) %>% 
  pivot_longer(c('cv_metric_AUC', "AUC"), 
               names_to = 'term', values_to = 'estimate') %>% 
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
         ) 
perf_100_plot <- perf_dat_100 %>% 
  ggplot(aes(x = estimate, y = outcome, color = term)) +
  geom_vline(xintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  xlim(0,1) +
  facet_wrap('dataset', ncol = 1) +
  coord_flip() +
  theme_sovacool() +
  theme(legend.position = 'top')
perf_100_plot
```

>>>>

```{r perf_100x}
perf_dat_100 <- data.table::fread(here('results', 
                                      'performance_results_aggregated.csv')
                                 ) %>% 
  pivot_longer(c('cv_metric_AUC', "AUC"), 
               names_to = 'term', values_to = 'estimate') %>% 
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
         ) 
perf_100_plot <- perf_dat_100 %>% 
  ggplot(aes(x = estimate, y = outcome, color = term)) +
  geom_vline(xintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  xlim(0,1) +
  facet_wrap('dataset', ncol = 1) +
  coord_flip() +
  theme_sovacool() +
  theme(legend.position = 'top')
perf_100_plot
```
```{r perf_temporal_vs_100}
cowplot::plot_grid(perf_temp_plot, perf_100_plot, nrow = 1)
```
